---
title: "Report"
author: Saskia Salzmann
editor: visual
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
    df-print: paged 
    embed-resources: true 
  pdf: 
    toc: true
  docx:
    toc: true
---

## Introduction

The aim of this exercise is to learn how to use GitHub and create a own report.

## Load Packages

```{r setup, include=FALSE}
library(psych)
library(tidyverse)
library(readxl)
library(here)
library(ggpubr)
```

## Data

These are data of my own PhD project. At the moment I look at the demographics of the data. That is why I added a simple graphic of the data points and a correlation .

```{r}
demo <- read_excel(here("data", "Lesion Size and Cognition_080324.xlsx"))
```

## Process data

```{r}
PS<-demo$VG_final
LS<-demo$`PIV (Percentage of infarct volume)`

```

## Visualisation

```{r}
ggplot(data = demo, mapping = aes(x = PS, y = LS)) + 
  labs(x = "Processing Speed", y = "Lesion size") +
  geom_point(alpha = 0.7, colour = "black", fill = "blue",
             shape = 21, size = 1.5, stroke = 1.0) +
  stat_cor(method = "spearman") +
  stat_smooth(method = lm)

```

## Conclusions

The correlation shows that the bigger the lesion size was, the worse the outcome of processing speed may be.
