---
title: "Lesion size and cognition in pediatric stroke patients"
author: Saskia Salzmann
editor: visual
format:
  html:
    toc: true
    code-fold: show
    code-tools: true
    df-print: paged 
    embed-resources: true 
  pdf: 
    toc: true
  docx:
    toc: true
---

## Introduction

Cognitive outcome after pediatric cancer is possible influenced by the size of the stroke lesion. In this study we analyse if lesion size may predict cognitive outcome in the long-term.

## Load Packages

```{r setup}
#| message: false
library(psych)
library(tidyverse)
library(readxl)
library(here)
library(ggpubr)
```

## Data

The data was collected in the neuropediatric stroke registry of Switzerland.

Current state: At the moment I analyse the demographics of the patients and some first correlations of different factors conducted.

```{r}
#| message: false
demo <- read_excel(here("data", "Lesion Size and Cognition_080324.xlsx"))
```

## Define factors

In the following visualization two variables will be included:

-   Lesion size

-   Processing speed (cognitive function)

```{r}
PS<-demo$VG_final
LS<-demo$`PIV (Percentage of infarct volume)`

```

## Visualisation

The graph shows the lesion size and the processing speed (two years after the stroke) of all the patients included in the analysis.

```{r}
ggplot(data = demo, mapping = aes(x = PS, y = LS)) + 
  labs(x = "Processing Speed", y = "Lesion size") +
  geom_point(alpha = 0.7, colour = "black", fill = "blue",
             shape = 21, size = 1.5, stroke = 1.0) +
  stat_cor(method = "spearman") +
  stat_smooth(method = lm)

```

## Conclusion

The correlation shows that the bigger the lesion size was, the worse the outcome of processing speed may be. It will be interesting to look deeper into the factors associated with lesion size and cognition.
